\begin{thebibliography}{99}
\begin{singlespace}
% Introductory
\bibitem{SAPS} B. Shakerighadi, S. Peyghami, E. Ebrahimzadeh, F. Blaabjerg and C. Leth Back, "A New Guideline for Security Assessment of Power Systems with a High Penetration of Wind Turbines," \textit{Applied Sciences}, vol. 10, no. 9, pp. 3190-3206, 2020.

\bibitem{I6} A. Mittal, J. Hazra, N. Jain, V. Goyal, D. Seetharam and Y. Sabharwal, "Real Time Contingency Analysis for Power Grids," in \textit{Proc. European Conference on Parallel Processing}, pp. 303-315, 2011, Berlin, Heidelberg.


%Literature Survey
\bibitem{L1} R. Zimmerman, C. Murillo-Sanchez and R. Thomas, "MATPOWER: Steady-State Operations, Planning, and Analysis Tools for Power Systems Research and Education," \textit{IEEE Transactions on Power Systems}, vol. 26, no. 1, pp. 12-19, 2011.
% previously
\bibitem{L2} H. Yang, K. Niu, D. Xu and S. Xu, "Analysis of power system transient stability characteristics with the application of massive transient stability simulation data," \textit{Energy Reports}, vol. 7, pp. 111-117, 2021. 

\bibitem{L3} I. Genc, Ruisheng Diao and V. Vittal, "Computation of transient stability related security regions and generation rescheduling based on decision trees," in \textit{Proc. IEEE PES General Meeting}, pp. 1-6, 25-29 July 2010, Minneapolis, MN, USA.

\bibitem{L4} L. Wehenkel, "Decision tree approach to power systems security assessment," \textit{International Journal of Electrical Power \& Energy Systems}, vol. 15, no. 1, pp. 13-36, 1993.

\bibitem{L5} L. Wehenkel and M. Pavella, "Decision trees and transient stability of electric power systems," \textit{Automatica}, vol. 27, no. 1, pp. 115-134, 1991. 
% ----------------
\bibitem{L6} Y. Zhang, W. Liu, Y. Huan, Q. Zhou and N. Wang, "Online Dynamic Total Transfer Capability Estimation Using Cotraining-Style Semi-Supervised Regression," \textit{IEEE Access}, vol. 8, pp. 94054-94064, 2020.

\bibitem{L7} S. Jafarzadeh, I. Genc and A. Nehorai, "Real-time transient stability prediction and coherency identification in power systems using Koopman mode analysis," \textit{Electric Power Systems Research}, vol. 201, pp. 107565-107577, 2021.

\bibitem{L8} M. Teixeira, I. Melo and J. Filho, "An optimisation model based approach for power systems voltage stability and harmonic analysis," \textit{Electric Power Systems Research}, vol. 199, pp. 107462-107473, 2021.

\bibitem{L9} L. Meegahapola, S. Bu, D. Wadduwage, C. Chung and X. Yu, "Review on Oscillatory Stability in Power Grids With Renewable Energy Sources: Monitoring, Analysis, and Control Using Synchrophasor Technology," \textit{IEEE Transactions on Industrial Electronics}, vol. 68, no. 1, pp. 519-531, 2021.

\bibitem{L10} Y. Chompoobutrgool, L. Vanfretti and M. Ghandhari, "Survey on power system stabilizers control and their prospective applications for power system damping using Synchrophasor-based wide-area systems," \textit{European Transactions on Electrical Power}, vol. 21, no. 8, pp. 2098-2111, 2011.

\bibitem{L11} S. Ghaedi, S. Abazari and G. Arab Markadeh, "Transient stability improvement of power system with UPFC control by using transient energy function and sliding mode observer based on locally measurable information," \textit{Measurement}, vol. 183, pp. 109842-109854, 2021. Available: 10.1016/j.measurement.2021.109842

\bibitem{L12} A. Sobbouhi and A. Vahedi, "Transient stability prediction of power system; a review on methods, classification and considerations," \textit{Electric Power Systems Research}, vol. 190, pp. 106853-106869, 2021.

\bibitem{L13} I. Kamwa, S. Samantaray and G. Joos, "Catastrophe Predictors From Ensemble Decision-Tree Learning of Wide-Area Severity Indices," \textit{IEEE Transactions on Smart Grid}, vol. 1, no. 2, pp. 144-158, 2010.

\bibitem{L15} W. Villa-Acevedo, J. López-Lezama, D. Colomé and J. Cepeda, "Long-term voltage stability monitoring of power system areas using a kernel extreme learning machine approach," \textit{Alexandria Engineering Journal}, vol. 61, no. 2, pp. 1353-1367, 2022.


% for print
%
%\bibitem{L2} H. Yang, K. Niu, D. Xu and S. Xu, "Analysis of power system transient stability characteristics with the application of massive transient stability simulation data," \textit{Energy Reports}, vol. 7, pp. 111-117, 2021. 
%
%\bibitem{L3} I. Genc, Ruisheng Diao and V. Vittal, "Computation of transient stability related security regions and generation rescheduling based on decision trees," in \textit{Proc. IEEE PES General Meeting}, pp. 1-6, 25-29 July 2010, Minneapolis, MN, USA.
%
%\bibitem{L4} L. Wehenkel, "Decision tree approach to power systems security assessment," \textit{International Journal of Electrical Power \& Energy Systems}, vol. 15, no. 1, pp. 13-36, 1993.
%
%\bibitem{L5} L. Wehenkel and M. Pavella, "Decision trees and transient stability of electric power systems," \textit{Automatica}, vol. 27, no. 1, pp. 115-134, 1991. 



% Project Motivation

\bibitem{1} S. Abhyankar, G. Geng, M. Anitescu, X. Wang and V. Dinavahi, "Solution techniques for transient stability‐constrained optimal power flow – Part I," \textit{IET Generation, Transmission \& Distribution}, vol. 11, no. 12, pp. 3177-3185, 2017.

\bibitem{2} G. Geng, S. Abhyankar, X. Wang and V. Dinavahi, "Solution techniques for transient stability‐constrained optimal power flow – Part II," \textit{IET Generation, Transmission \& }; Distribution, vol. 11, no. 12, pp. 3186-3193, 2017.

\bibitem{5} A. Sobbouhi and A. Vahedi, "Online synchronous generator out-of-step prediction by ellipse fitting on acceleration power – Speed deviation curve," \textit{International Journal of Electrical Power \& Energy Systems}, vol. 119, pp. 105965-105973, 2020.

\bibitem{I5} A. Sobbouhi and A. Vahedi, "Transient stability improvement based on out-of-step prediction," \textit{Electric Power Systems Research}, vol. 194, pp. 107108-107119, 2021.
%%%%%%%%%%%%%%%%
\bibitem{I3} M. Mynuddin, "Stability Study of Power System," \textit{International Journal of Energy and Power Engineering}, vol. 4, no. 2, pp. 43-51, 2015.

\bibitem{7} P. Kundur, N. J Balu and M. G Lauby, \textit{Power system stability and control}, 7th ed. Electrical Power Research Institute, New York: McGraw-Hill Professional, 1994.

\bibitem{8} G. Ravikumar and S. Khaparde, "Taxonomy of PMU Data Based Catastrophic Indicators for Power System Stability Assessment," \textit{IEEE Systems Journal}, vol. 12, no. 1, pp. 452-464, 2018.

\bibitem{9} H. Hashim, I. Abidin, H. Rashid, N. Zulkapli, S. Ibrahim, S. Kamar and N. Sofizan, "An out-of-step detection based on transient stability index," \textit{Aust. J. Basic Appl. Sci.}, vol. 7, no. 4, pp. 353-365, 2013.
%
\bibitem{EPM} C. Fu and A. Bose, "Contingency ranking based on severity indices in dynamic security analysis," \textit{IEEE Transactions on Power Systems}, vol. 14, no. 3, pp. 980-985, 1999. Available: 10.1109/59.780910
%
\bibitem{CSA} I. Kamwa, R. Grondin and L. Loud, "Time-varying contingency screening for dynamic security assessment using intelligent-systems techniques," \textit{IEEE Transactions on Power Systems}, vol. 16, no. 3, pp. 526-536, 2001.
%
\bibitem{CSA_WASI} I. Kamwa, S. Samantaray and G. Joos, "Development of Rule-Based Classifiers for Rapid Stability Assessment of Wide-Area Post-Disturbance Records," \textit{IEEE Transactions on Power Systems}, vol. 24, no. 1, pp. 258-270, 2009.

\bibitem{ISPI} O. Gomez and M. Rios, "Inter-area stability prediction index based on phasorial measurement," in \textit{Proc. IEEE PES Innovative Smart Grid Technologies (ISGT)}, pp. 1-8, 16-20 Jan. 2012, Washington, DC, USA.
%
\bibitem{MattransSoft} G. Ravikumar, "\textit{MATTRANS: a MATLAB power system transient stability simulation package}", 2016. [Online]. Available: https://github.com/gelliravi/MatTrans.
%
\bibitem{FR1} R. Green, L. Wang and M. Alam, "High performance computing for electric power systems: Applications and trends," in \textit{Proc. IEEE Power and Energy Society General Meeting}, pp. 1-8, 24-28 July 2011, Detroit, MI, USA.
%
\bibitem{FR2} V. Jalili-Marandi, Zhiyin Zhou and V. Dinavahi, "Large-scale transient stability simulation of electrical power systems on parallel GPUs," in \textit{Proc. IEEE Power and Energy Society General Meeting}, pp. 1-11, 22-26 July 2012, San Diego, CA, USA.
%
%
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
%
%\bibitem{}
\end{singlespace}

\end{thebibliography}